\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-06-27 src/algorithm.tex
fix errors

Let $\~c$ be the maximum cost incurs by embedding a single virtual node into 
a physical node in an optimal embedding, 
that is $\~c \eqdf \max_{\alpha \in \calV}c(\alpha, f_{opt}(\alpha))$.
Given $\varepsilon$ we define 
$$
c'(\alpha, v) \eqdf
\begin{cases}
\ceil{c(\alpha, v)/\mu} & c(\alpha, v) \leq \~c
\\
\infty & c(\alpha, v) > \~c
\end{cases}
$$
where 
$
\mu \eqdf \frac{\~c\varepsilon}{n}
$.
Let $s$ be an optimal placement w.r.t $c'$ 
and let $o$ be an optimal placement w.r.t $c$, 
let also $S$ and $O$ denotes their values respectively, then.
\begin{lemma}
S \leq (1 + \varepsilon)O
\end{lemma}
\begin{proof}
\begin{align*}
S = & \sum_{\alpha \in \calV}c(\alpha, s(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c'(\alpha, s(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c'(\alpha, o(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c(\alpha, o(\alpha))/\mu + 1 \leq
\\&
\sum_{\alpha \in \calV}c(\alpha, o(\alpha)) + n\mu =
O + \~c\varepsilon \leq (1 + \varepsilon)O
\end{align*}
\end{proof}
Clearly, $\~c$, is not known in advanced, but one can "guess" 
its value as there are at most
$|\calV| \cdot |V|$ possible values to choose from.

>>>>

Let $\hat{c}$ be the maximum cost incurs by embedding a single virtual node into 
a physical node in an optimal embedding, 
that is $\hat{c} \eqdf \max_{\alpha \in \calV}c(\alpha, f_{opt}(\alpha))$.
Given $\varepsilon$ we define 
$$
c'(\alpha, v) \eqdf
\begin{cases}
\ceil{c(\alpha, v)/\mu} & c(\alpha, v) \leq \hat{c}
\\
\infty & c(\alpha, v) > \hat{c}
\end{cases}
$$
where 
$
\mu \eqdf \frac{\hat{c}\varepsilon}{n}
$.
Let $s$ be an optimal placement w.r.t $c'$ 
and let $o$ be an optimal placement w.r.t $c$, 
let also $S$ and $O$ denotes their values respectively, then.
\begin{lemma}
S \leq (1 + \varepsilon)O
\end{lemma}
\begin{proof}
\begin{align*}
S = & \sum_{\alpha \in \calV}c(\alpha, s(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c'(\alpha, s(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c'(\alpha, o(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c(\alpha, o(\alpha))/\mu + 1 \leq
\\&
\sum_{\alpha \in \calV}c(\alpha, o(\alpha)) + n\mu =
O + \hat{c}\varepsilon \leq (1 + \varepsilon)O
\end{align*}
\end{proof}
Clearly, $\hat{c}$, is not known in advanced, but one can "guess" 
its value as there are at most
$|\calV| \cdot |V|$ possible values to choose from.
